Details of specific functions

### 2017-08-21 inst/gitbook/03_specific-tutorials.Rmd
Gitbook!
removed hyper.volume

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
1 | `hypervolume` | The volume of the ordinated space | [`hypervolume`](https://cran.r-project.org/web/packages/hypervolume/index.html)`::hypervolume` |
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
2 | `variances` | The variance of each dimension | `dispRity` |
2 | `centroids`<sup>2</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `mode.val` | The modal value | `dispRity` |

@@

#### Volumes and surface metrics
The functions `ellipse.volume`, `convhull.surface`, `convhull.volume` and `hyper.volume` all measure the surface or the volume of the ordinated space occupied:

@@

The convex hull functions make a (good) estimation of the multidimensional properties of the ordinated space.
For the full and correct calculation of the volume of the ordinated space, it is possible to use the `hyper.volume` function that has more options but takes longer to calculate.

```{r}
## Calculating the true multidimensional volume
summary(dispRity(dummy_space, metric = hyper.volume))

```
> Cautionary note: measuring volumes in a high number of dimensions can be strongly affected by the [curse of dimensionality](https://en.wikipedia.org/wiki/Curse_of_dimensionality) that often results in near 0 disparity values.

@@

### `space.maker`
Another way to simulate data is to directly simulate an ordinated space with the `space.maker` function.
This function allows users to simulate multidimensional spaces with a certain number of properties.
It takes as arguments the number of elements (data points) and dimensions to create the space but also permits more fine tuning in the data simulation: it is possible to give a specific distribution to each dimension, provide a correlation matrix to link the dimensions or even provide an *a priori* distribution of the variance for each distributions!
<!-- ooh fancy! -->

>>>>

Level | Name | Description | Source | 
------|------|---------------------------------------------------|--------|
1 | `ellipse.volume`<sup>1</sup> | The volume of the ellipsoid of the space | Donohue _et al._ (2013) |
1 | `convhull.surface` | The surface of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
1 | `convhull.volume` | The volume of the convex hull formed by all the elements | [`geometry`](https://cran.r-project.org/web/packages/geometry/index.html)`::convhulln` |
<!-- 1 | `hypervolume` | The volume of the ordinated space | [`hypervolume`](https://cran.r-project.org/web/packages/hypervolume/index.html)`::hypervolume` |-->
1 | `diagonal` | The longest distance in the ordinated space (like the diagonal in two dimensions) | `dispRity` |
2 | `ranges` | The range of each dimension | `dispRity` |
2 | `variances` | The variance of each dimension | `dispRity` |
2 | `centroids`<sup>2</sup> | The distance between each element and the centroid of the ordinated space | `dispRity` |
1 | `mode.val` | The modal value | `dispRity` |

@@

#### Volumes and surface metrics
The functions `ellipse.volume`, `convhull.surface` and `convhull.volume`  all measure the surface or the volume of the ordinated space occupied:

@@

The convex hull functions make a (good) estimation of the multidimensional properties of the ordinated space.

> Cautionary note: measuring volumes in a high number of dimensions can be strongly affected by the [curse of dimensionality](https://en.wikipedia.org/wiki/Curse_of_dimensionality) that often results in near 0 disparity values.

@@

## Simulating multidimensional spaces
Another way to simulate data is to directly simulate an ordinated space with the `space.maker` function.
This function allows users to simulate multidimensional spaces with a certain number of properties.
It takes as arguments the number of elements (data points) and dimensions to create the space but also permits more fine tuning in the data simulation: it is possible to give a specific distribution to each dimension, provide a correlation matrix to link the dimensions or even provide an *a priori* distribution of the variance for each distributions!
<!-- ooh fancy! -->
